### 2019-04-15 paper/paper.tex
added related works section (could be expanded)

\textbf{Takeaways.} We find that while the \code{npm} ecosystem
continues to grow, the rate of growth is no longer superlinear, 
a possible sign of the ecosystem beginning to reach some form of maturity.
In the relationships between packages, we find that though the average number
of dependencies continues to grow, there has been a recent decline in the
rate of this growth. Accordingly, we have found that the number of packages with
zero dependencies has increased from 28.7\% in September 2015 to [DATA REQUIRED]\%
as of April 2019. The percentage of packages that are depended on has
also declined, albeit still exhibiting a power law relationship as observed
in prior software ecosystem research \cite{Wittern:2016, Myers:2003, Louridas:2008}.

@@

\subsection{Attribution of Version Numbers}
[NEEDS MORE DATA]

@@

\section{Related Work}
[IN PROGRESS]

@@

@@

@@

@@

@@

@@

>>>>

\textbf{Takeaways.} We find that while the \code{npm} ecosystem
continues to grow, the rate of growth is no longer superlinear, 
a possible sign of the ecosystem beginning to reach some form of maturity \cite{Alves:2011}.
In the relationships between packages, we find that though the average number
of dependencies continues to grow, there has been a recent decline in the
rate of this growth. Accordingly, we have found that the number of packages with
zero dependencies has increased from 28.7\% in September 2015 to [DATA REQUIRED]\%
as of April 2019. The percentage of packages that are depended on has
also declined, albeit still exhibiting a power law relationship as observed
in prior software ecosystem research \cite{Wittern:2016, Myers:2003, Louridas:2008}.

@@

\subsection{Attribution of Version Numbers}
[NEEDS MORE DATA

@@

\section{Related Work}

Related research can be generally described as one of two types
of work: meta-analyses of the behaviour and importance
of software ecosystems, and empirical investigations into the
specifics of a particular ecosystem. Some topics 
for meta-analyses include ecosystem visualization \cite{LUNGU2010264},
ecosystem maturity \cite{Alves:2011}, quality metric aggregation \cite{Mordal:2013},
and literature reviews \cite{Manikas:2013, Manikas:2017}. Specific ecosystem analysis include works such
paper and the original research by Wittern, Suter and Rajagopalan \cite{Wittern:2016} on \code{npm}.
Others have performed evaluations of specific ecosystems such as Raemaekers et al. \cite{Raemaekers:2013},
who present a dataset with basic metrics, dependencies and changes within the popular 
Java-based Maven ecosystem. Another work investigates the
result of changing project interdependencies in Apache \cite{Bavota:2013}, 
and still others evaluate evolution over time in ecosystems such as
Gentoo \cite{Bloemen:2014}, Ruby, \cite{Kabbedijk:2011}, and R \cite{Plakidas:2017}.

@@

  \bibitem{Alves:2011}
  Salviano~C.F Alves~A.M., Pessoa~M.
  \newblock {\em Towards a Systemic Maturity Model for Public Software
    Ecosystems}, volume 155.
  \newblock Springer, Berlin, Heidelberg, 2011.

  \bibitem{Bavota:2013}
  Gabriele Bavota, Gerardo Canfora, Massimiliano~Di Penta, Rocco Oliveto, and
    Sebastiano Panichella.
  \newblock The evolution of project inter-dependencies in a software ecosystem:
    The case of apache.
  \newblock In {\em Proceedings of the 2013 IEEE International Conference on
    Software Maintenance}, ICSM '13, pages 280--289, Washington, DC, USA, 2013.
    IEEE Computer Society.

@@

  \bibitem{Bloemen:2014}
  Remco Bloemen, Chintan Amrit, Stefan Kuhlmann, and Gonzalo Ordonez-Matamoros.
  \newblock Gentoo package dependencies over time.
  \newblock pages 404--407, 05 2014.

@@

  \bibitem{Kabbedijk:2011}
  Jaap Kabbedijk and Slinger Jansen.
  \newblock Steering insight: An exploration of the ruby software ecosystem.
  \newblock volume~80, pages 44--55, 06 2011.

@@

  \bibitem{Mordal:2013}
  Karine Mordal-Manet, Nicolas Anquetil, Jannik Laval, Alexander Serebrenik,
    Bogdan Vasilescu, and Stéphane Ducasse.
  \newblock Software quality metrics aggregation in industry.
  \newblock {\em Journal of Software: Evolution and Process}, 25:1117--1135, 10
    2013.

@@

  \bibitem{Plakidas:2017}
  Konstantinos Plakidas, Daniel Schall, and Uwe Zdun.
  \newblock Evolution of the r software ecosystem.
  \newblock {\em J. Syst. Softw.}, 132(C):119--146, October 2017.

@@

  \bibitem{Raemaekers:2013}
  Steven Raemaekers, Arie van Deursen, and Joost Visser.
  \newblock The maven repository dataset of metrics, changes, and dependencies.
  \newblock pages 221--224, 05 2013.
